How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-16 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

>>>>

A related paper has criticised vague statistical methods sections because they deprive readers and reviewers for the opportunity to confirm that the appropriate methods were used [@Weissgerber2018]. These authors checked hundreds of papers using ANOVA and found that 95\% did not contain the information needed to determine what type of ANOVA was performed. This lack of information could well be because the authors used a boilerplate statistical methods section that was missing key details.

If authors shared their code then this would provide an alternative route for checking what statistical methods were used. This is not a perfect solution, as we still want authors to accurately report their methods, but it does increase transparency. However, a recent paper found that code sharing was very low in biomedical papers, with just 2\% of a sample of over 6,000 papers sharing code [@Serghiou2021].
